Comparing top performing models

### 2019-04-07 Scripts/evaluating_models_with_dist_preds.Rmd
editted results scripts

## SMOTE

### GM12878

```{r}

###10kb
rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_gm12878_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_gm12878_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_gm12878_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

@@

### K562

```{r}

###10kb
rfperf_k562_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_k562_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_k562_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_k562_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

>>>>

##gm12878

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
                                                        rep("25 kb", 12),
                                                        rep("50 kb", 12),
                                                        rep("100 kb", 12)),4),
                                       Predictor=rep(c("OC","OP","Distance"),64),
                                       Metric=c(rep("AUC",48),
                                                rep("AUPRC",48),
                                                rep("F1-Score",48), 
                                                rep("MCC",48)),
                                       Resampling=rep(c(rep("None",3),
                                                    rep("ROS",3),
                                                    rep("RUS",3),
                                                    rep("SMOTE",3)),16))
all_rfperfs_gm12878$Resolution <- factor(all_rfperfs_gm12878$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))

all_rfperfs_gm12878$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc

                                     round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc

                                     round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc

                                     round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2) #mcc
)

p1 <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="Distance"),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
    geom_line(size=2)+
    geom_point(size=5)+
    facet_grid(~ Metric)+
    theme_minimal() +
    theme_bw()+
    xlab("") + ylab("") +
  scale_color_discrete(name="Re-Sampling Technique")+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
	      plot.title = element_text(size=20))

@@

##k562

```{r}
#OC
##None
rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_K562_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_K562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
